MONID

### 2023-09-20 Presentation/presentation.tex
update

    \begin{block}{Note.}    
        The difference between maximal and minimal interpretation becomes important only when we are evaluating the at the boundaries of a trace; $\underline{\text{max}}$ rules evaluates at $\underline{\text{true}}$ at initial and final istants, while $\underline{\text{min}}$ rules evaluates at $\underline{\text{false}}$.
    \end{block}    
\end{frame}

@@

\begin{frame}
    \frametitle{Port Scanning attacks}
    \textit{Port scanning} is a method used to identify exploitable communication channels in networks; it involves probing network ports and keeping useful information for attacks. The victim machine suspect port scans as malicious when the counter of reached ports exceeds a specific threshold. The formulas are the following:
    \begin{align*}
        & \underline{\text{max}}\ \mathtt{NewPort}(\underline{\text{string}}\ i1,\underline{\text{string}}\ i2,\underline{\text{Set}}\ S) = (i1=ip1)\land(i2=ip2)\land (port \notin S)\\
        & \underline{\text{max}}\ \mathtt{Counter}(\underline{\text{long}}\ t, \underline{\text{long}}\ d, \underline{\text{int}}\ c,\underline{\text{string}}\ i1,\underline{\text{string}}\ i2,\underline{\text{Set}}\ S,\underline{\text{int}}\ C) = (time-t<d)\\
        & \quad\quad\rightarrow((\mathtt{NewPort}(i1,i2,S)\rightarrow(c\leq C\land \bigcirc\mathtt{Counter}(t,d,c+1,i1,i2,S\cup\{port\},C)))  \\
        & \quad\quad\land(\neg \mathtt{NewPort}(i1,i2,S)\rightarrow\mathtt{Counter}(t,d,c,i1,i2,S,C))) \\
        & \underline{\text{mon}}\ \mathtt{PortScanSafe} =\ \mathtt{Always}(\mathtt{Counter}(time,100,1,ip1,ip2,\{port\},10)) 
    \end{align*}
    where we checks if the number of port scans between $ip1,ip2$ does not exceed a threshold of $10$ within $100$ seconds.
\end{frame}

>>>>

    \begin{block}{Note.}    
        The difference between maximal and minimal interpretation becomes important only when we are evaluating the at the boundaries of a trace; $\underline{\text{max}}$ rules evaluates at $\underline{\text{true}}$ at initial and final istants, while $\underline{\text{min}}$ rules evaluates at $\underline{\text{false}}$.
    \end{block}    
    \newpage
    To better understand the mechanism, let us introduce an example.\\ Given the definition 
    \begin{align*}
        & \underline{\text{min}}\ \mathtt{Property}(\underline{\text{Form}}\ F) =F \lor \bigcirc \mathtt{Property}(F)
    \end{align*} 
    and the sequence $\sigma=\alpha_{1},\ldots ,\alpha_{n}$, $\mathtt{Property}$ will evaluate to \textit{true} 
    \begin{align*}
        & evaluate(\ldots evaluate(evaluate(\mathtt{Property},\alpha_1),\alpha_2),\ldots,\alpha_n)=true
    \end{align*}
    if and only if the rule is true at some given event $\alpha_i$. Once the sequence has been completely analyzed, we will obtain the following big disjunction: 
    \begin{align*}
        & F \lor \bigcirc(F \lor \bigcirc(\ldots F \lor \bigcirc \mathbf{Property(F)})) 
    \end{align*}
    $\mathbf{Property(F)}$ will be evaluated as false since it is the last of a big disjunction and we want to close it.

@@

\begin{frame}
    \frametitle{Port Scanning attacks}
    \textit{Port scanning} is a method used to identify exploitable communication channels in networks; it involves probing network ports and keeping useful information for attacks. The victim machine suspect port scans as malicious when the counter of reached ports exceeds a specific threshold. The formulas are the following:
    \begin{align*}
        & \underline{\text{max}}\ \mathtt{NewPort}(\underline{\text{string}}\ i1,\underline{\text{string}}\ i2,\underline{\text{Set}}\ S) = (i1=ip1)\land(i2=ip2)\land (port \notin S)\\
        & \underline{\text{max}}\ \mathtt{Counter}(\underline{\text{long}}\ t, \underline{\text{long}}\ d, \underline{\text{int}}\ c,\underline{\text{string}}\ i1,\underline{\text{string}}\ i2,\underline{\text{Set}}\ S,\underline{\text{int}}\ C) = (time-t<d)\\
        & \quad\quad\rightarrow((\mathtt{NewPort}(i1,i2,S)\rightarrow(c\leq C\land \bigcirc\mathtt{Counter}(t,d,c+1,i1,i2,S\cup\{port\},C)))  \\
        & \quad\quad\land(\neg \mathtt{NewPort}(i1,i2,S)\rightarrow\mathtt{Counter}(t,d,c,i1,i2,S,C))) \\
        & \underline{\text{mon}}\ \mathtt{PortScanSafe} =\ \mathtt{Always}(\mathtt{Counter}(time,100,1,ip1,ip2,\{port\},10)) 
    \end{align*}
    where we checks if the number of (new) port scans between $ip1,ip2$ does not exceed a threshold of $10$ within $100$ seconds.
\end{frame}
